\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}

\title{Sorting Algorithms}
\author{Alejandro Ferrer}
\date{05/17/2019}

\begin{document}
\maketitle

In this assignment I was able to test different types of sorting algorithms in order to analyze their performance. 
In this case I used four different algorithms: Bubble Sort, Selection Sort, Insertion Sort and Quick Sort--

\begin{itemize}
  \item Bubble Sort consists in a simple algorithm that works by swapping elements if they are in the wrong order. 
  \item Inserion Sort builds the final arrangement one element at a time. It is not very efficient in large lists.
  
  \item Selection Sort rearranges the array by finding the smallest value of the unsorted array and puts it on a subarray of sorted elements. It repeats this process until the sorted list is completed.
  \item Quick Sort is a Divide and Conquer algorithm. It finds a pivot point and then it partitions the array from the pivot point into two parts.

\end{itemize}

Throughout this assignment I implemented all of these sorting algorithms using a data sample with 10000 different numbers. The results indicate that Bubble sort is the slowest one in terms of run time but it has a very simple implementation. Selection sorting and Insertion Sorting were roughly the same in amount of time to sort. Finally, Quick sort was the fastest of all four algorithms but I had to use one more method to implement it.

\end{document}
